---
output: pdf_document
---

```{r do_work, include=FALSE}
##code block do_work does most of the data processing.  Code is hidden from user, only make dataframes for future use
##command arguements
##Argument 1 is NDVI file
##argument 2 is IRT file

#set options
options(digits=12)
#get the basename of each file
nameIRT=sub("^([^.]*).*", "\\1", basename(dataPathIRT)) 
nameNDVI=sub("^([^.]*).*", "\\1", basename(dataPathNDVI))

##read both NDVI and IRT file
dataNDVI=read.table(paste(cur, dataPathNDVI, sep="/"), header=TRUE)
dataIRT=read.table(paste(cur, dataPathIRT,sep="/"), header=TRUE)

#Find height and width to scale graphing
height=max(dataNDVI$absolute_sensor_position_y)-min(dataNDVI$absolute_sensor_position_y)
width=max(dataNDVI$absolute_sensor_position_x)-min(dataNDVI$absolute_sensor_position_x)
#get a ratio of height and width to scale graphs with
ratio=width/height

##find average values to find experiment.  Used to find experiment may change to median in the future
avgx=mean(dataNDVI$absolute_sensor_position_x)
avgy=mean(dataNDVI$absolute_sensor_position_y)

##go to the database find experiment that falls within plots
#Create connection to KSU WheatGenetics server
require(DBI)
require(RMySQL)
#connect to the database
#con=dbConnect(MySQL(),  user='wheatgeneticist', password="password", dbname='wheatgenetics', host='apate', port=6306)
con=dbConnect(MySQL(),  user='wheatgeneticist', password="password", dbname='wheatgenetics', host='apate')


##find experiment based on average values
##!!!may need to update this to include year
#write sql statement with variables
sqlStatement = paste("select e.* from experiment e where e.C1_1_x <", avgx, " and e.C1_2_x >", avgx,"and e.C1_1_y <", avgy, "and e.C2_1_y >", avgy, "and e.experiment_id like '15%'", sep=" ")
#perform query
experiment=dbGetQuery(con, sqlStatement)

#get experiment_id for future use
experiment_id=experiment$experiment_id

##query plots that have the experiment_id by making sql statement
sqlStatementPlots = paste("select pm.* from plot_map pm right join plot p  on pm.plot_id = p.plot_id where p.experiment_id = '", experiment_id,"'" ,sep="")

##query the database
plots=dbGetQuery(con, sqlStatementPlots)

#detach RMySQL
detach("package:RMySQL", unload=TRUE)

#load sqldf
require(sqldf)
##asssign data to plots using sqldf and the plots NDVI/IRT dataframes
assignedNDVI=sqldf("select d.*, b.* from dataNDVI d, plots b where d.absolute_sensor_position_x > b.C1_1_x and d.absolute_sensor_position_x < b.C1_2_x and d.absolute_sensor_position_y > b.C1_1_y and d.absolute_sensor_position_y < C2_1_y")
assignedIRT=sqldf("select d.*, b.* from dataIRT d, plots b where d.absolute_sensor_position_x > b.C1_1_x and d.absolute_sensor_position_x < b.C1_2_x and d.absolute_sensor_position_y > b.C1_1_y and d.absolute_sensor_position_y < C2_1_y")

#require plyr
require(plyr)
##change data frame to assigned_data, separate based on plot name and calculate within plot paramenter
sum_assigned_NDVI=ddply(assignedNDVI, .(plot_id), .fun=function(x){
  #minimum observation
  MinOb=round(min(x$sensor_observation), 2)
  #max observation rounded to two decimal places
  MaxOb=round(max(x$sensor_observation),2)
  #average observtion per plot
  MeanOb=round(mean(x$sensor_observation),2)
  #variance per plot with 4 decimals
  Variance=round(var(x$sensor_observation),4)
  #standard deviaiton per plot 
  STDEV=round(sd(x$sensor_observation),2)
  #coefficient of varioatn per plot
  CV=round((sd(x$sensor_observation)/mean(x$sensor_observation))*100,2)
  #number of observations per plot
  NumObs=nrow(x)
  #sensor ID
  sensor_ID=as.character(x$sensor_ID[1])
  #sampling date
  sampling_Date=as.character(x$sampling_Date[1])
  #return data frame with above information
  return(c(MinOb, MaxOb, MeanOb, Variance,STDEV, CV, NumObs, sensor_ID, sampling_Date))
})

colnames(sum_assigned_NDVI)=c("plot_id","MinOb", "MaxOb", "MeanOb","Variance", "STDEV", "CV", "NumObs", "sensor_ID", "sampling_Date")
sum_assigned_NDVI$MinOb=as.numeric(sum_assigned_NDVI$MinOb)
sum_assigned_NDVI$MaxOb=as.numeric(sum_assigned_NDVI$MaxOb)
sum_assigned_NDVI$MeanOb=as.numeric(sum_assigned_NDVI$MeanOb)
sum_assigned_NDVI$Variance=as.numeric(sum_assigned_NDVI$Variance)
sum_assigned_NDVI$STDEV=as.numeric(sum_assigned_NDVI$STDEV)
sum_assigned_NDVI$CV=as.numeric(sum_assigned_NDVI$CV)
sum_assigned_NDVI$NumObs=as.numeric(sum_assigned_NDVI$NumObs)


sum_assigned_IRT=ddply(assignedIRT, .(plot_id), .fun=function(x){
  #minimum observation
  MinOb=round(min(x$sensor_observation), 2)
  #max observation rounded to two decimal places
  MaxOb=round(max(x$sensor_observation),2)
  #average observtion per plot
  MeanOb=round(mean(x$sensor_observation),2)
  #variance per plot with 4 decimals
  Variance=round(var(x$sensor_observation),4)
  #standard deviaiton per plot 
  STDEV=round(sd(x$sensor_observation),2)
  #coefficient of varioatn per plot
  CV=round((sd(x$sensor_observation)/mean(x$sensor_observation))*100,2)
  #number of observations per plot
  NumObs=nrow(x)
  #sensor ID
  sensor_ID=as.character(x$sensor_ID[1])
  #sampling date
  sampling_Date=as.character(x$sampling_Date[1])
  #return data frame with above information
  return(c(MinOb, MaxOb, MeanOb, Variance,STDEV, CV, NumObs, sensor_ID, sampling_Date))
})

colnames(sum_assigned_IRT)=c("plot_id","MinOb", "MaxOb", "MeanOb","Variance", "STDEV", "CV", "NumObs", "sensor_ID", "sampling_Date")
sum_assigned_IRT$MinOb=as.numeric(sum_assigned_IRT$MinOb)
sum_assigned_IRT$MaxOb=as.numeric(sum_assigned_IRT$MaxOb)
sum_assigned_IRT$MeanOb=as.numeric(sum_assigned_IRT$MeanOb)
sum_assigned_IRT$Variance=as.numeric(sum_assigned_IRT$Variance)
sum_assigned_IRT$STDEV=as.numeric(sum_assigned_IRT$STDEV)
sum_assigned_IRT$CV=as.numeric(sum_assigned_IRT$CV)
sum_assigned_IRT$NumObs=as.numeric(sum_assigned_IRT$NumObs)

#Functions
##expgraph makes a blank plot of the area in the data set
expgraph=function(x){
  #Plots using maximum and minimum UTM coordinates, creates blank plot
  with(x, plot(absolute_sensor_position_x, absolute_sensor_position_y, type="n", main="", xlab="UTM East", ylab="UTM North", xlim=c(min(absolute_sensor_position_x)-1, max(absolute_sensor_position_x))+1, ylim=c(min(absolute_sensor_position_y), max(absolute_sensor_position_y))))
  #with(x, north.arrow(xb=(max(absolute_sensor_position_x)+0.75), yb=(max(absolute_sensor_position_y)-2), len=.25, tcol="black", lab="N", cex.lab=.75))
  #need to have GISTools for north arrow to work, I have had problems loading the package on server
}

#function to graph NDVI which ranges from 0 to 1 by color rainbow for value
gspoints=function(x){
  with(x, points(absolute_sensor_position_x, absolute_sensor_position_y, col=rainbow(1000)[sensor_observation*1000], cex=0.2))
  
}

#function to graph infrared points by binning temperatures
irpoints=function(x){
  bins=cut(x$sensor_observation, c(-Inf,25, 27, 28, 29, 30, 31,32,33,34,35,37,39,42, Inf ))
  with(x, points(absolute_sensor_position_x, absolute_sensor_position_y, col=rainbow(14)[bins], cex=0.2))
}
plot_boundary=function(x){
  for (i in 1:nrow(x)){
    #using the sonar data plot a polygon using the four corners
    with(x, polygon(x=c(C2_1_x[i], C2_2_x[i], C1_2_x[i], C1_1_x[i]), y=c(C2_1_y[i], C2_2_y[i], C1_2_y[i], C1_1_y[i]), border="black"))
  }
}

##this add a plot label, label can be decided from existing column of data frame
plot_label=function(x="dataframe", y="df$colname"){
  for(i in 1:nrow(x)){
    with(x, text(x=((C2_1_x[i]+C2_2_x[i])/2), y=((C2_1_y[i]+ C1_2_y[i])/2), labels=paste(y[i], sep="\n"), cex=0.75))
  }
}
```

---
title: "`r paste("Data Summary for ", experiment_id, sep="")`"
author: "Jared Crain"
date: "`r Sys.Date()`"

---

Summary:  For Phenocorn run on `r dataNDVI$sampling_Date[1]` there were `r nrow(dataNDVI)` data points.  Of the `r nrow(dataNDVI)` observations, `r nrow(assignedNDVI)` data points were assigned to geo-referenced plots.  These observations correspond to the `r experiment_id` trial which has `r nrow(plots)` plots.  

Location:  
```{r google_map_location, echo=FALSE, fig.width=7, fig.height=7, warning=FALSE, message=FALSE}
require(ggmap)
require(rgdal)
#function to convert UTM experiment coordinates to Lat long to graph on GOOGLE earth
experiment_lat_long=function(x){
# prepare UTM coordinates matrix
CRSstring=paste("+proj=utm +zone=", x$long_zone, sep="")
utmcoor1<-SpatialPoints(cbind(x$C1_1_x,x$C1_1_y), proj4string=CRS("+proj=utm +zone=12 +ellps=WGS84"))
utmcoor2<-SpatialPoints(cbind(x$C1_2_x,x$C1_2_y), proj4string=CRS("+proj=utm +zone=12 +ellps=WGS84"))
utmcoor3<-SpatialPoints(cbind(x$C2_1_x,x$C2_1_y), proj4string=CRS("+proj=utm +zone=12 +ellps=WGS84"))
utmcoor4<-SpatialPoints(cbind(x$C2_2_x,x$C2_2_y), proj4string=CRS("+proj=utm +zone=12 +ellps=WGS84"))
#utmdata$X and utmdata$Y are corresponding to UTM Easting and Northing, respectively.
#zone= UTM zone
# converting
utmcoor1r<-spTransform(utmcoor1,CRS("+proj=longlat +ellps=WGS84"))
utmcoor2r<-spTransform(utmcoor2,CRS("+proj=longlat +ellps=WGS84"))
utmcoor3r<-spTransform(utmcoor3,CRS("+proj=longlat +ellps=WGS84"))
utmcoor4r<-spTransform(utmcoor4,CRS("+proj=longlat +ellps=WGS84"))
experiment=cbind(x, utmcoor1r, utmcoor2r, utmcoor3r, utmcoor4r)
colnames(experiment)[23:30]=c("Long1", "Lat1", "Long2", "Lat2", "Long3", "Lat3", "Long4", "Lat4")
return(experiment)}
experiment=experiment_lat_long(experiment)
a=get_map(location=c(lon=mean(dataNDVI$left_long), lat=mean(dataNDVI$left_lat) ), zoom=19, maptype="satellite", source="google")

##function makes a map color coded by NDVI value with experiment border included in white
ggmap(a )+geom_point( aes(x = dataNDVI$left_long, y = dataNDVI$left_lat, col=dataNDVI$sensor_observation ), size=0.5,data = dataNDVI, alpha = .5)+theme(legend.position="none")+scale_colour_gradientn(colours = rainbow(8))+geom_path(aes(x=c(experiment$Long1,experiment$Long2, experiment$Long4 ,experiment$Long3, experiment$Long1), y=c(experiment$Lat1,experiment$Lat2, experiment$Lat4, experiment$Lat3, experiment$Lat1)), linejoin = "round",col="white", size=0.8 ,data=experiment)



```

\pagebreak

Tabular statistics for the NDVI data are:

```{r summary_statNDVI, echo=FALSE}
summary(dataNDVI[,2])
```

```{r NDVI_Graph, echo=FALSE, fig.width=12*ratio, fig.height=12}
expgraph(dataNDVI)
gspoints(dataNDVI)
plot_boundary(plots)
title(main=experiment_id, sub=dataNDVI$sampling_Date[1])
```
\pagebreak

Tabular statistics for IRT data:

```{r summary_statIRT, echo=FALSE}
summary(dataIRT[,2])
```

```{r, echo=FALSE, fig.width=12*ratio, fig.height=12}
expgraph(dataNDVI)
irpoints(dataIRT)
plot_boundary(plots)
title(main=experiment_id, sub=dataIRT$sampling_Date[1])
```

\pagebreak

Plot level statistics:

NDVI plot level data:

```{r, plot_level_NDVI, global.par=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8, fig.width=8}
require(plyr)
if(nrow(plots) > 50){
  d_ply(sum_assigned_NDVI, .(), .fun=function(x){
    par(mfrow=c(2,2))
  hist(x$MeanOb, main=paste("Sensor", x$sensor_ID[1], experiment_id , sep= " "), sub=paste(x$sampling_Date[1] ,sep=" ") ,ylab="Number of Plots", xlab="Mean Observation", cex=0.75) 
##  hist(x$Variance, main=paste("Sensor", x$sensor_ID[1], experiment_id, sep=" "),sub=paste(x$sampling_Date[1] ,sep=" ") ,ylab="Number of Plots", xlab="Variance of plosts", cex=0.75)
 hist(x$STDEV, main=paste("Sensor", x$sensor_ID[1], experiment_id , sep= " "), sub=paste( x$sampling_Date[1] ,sep=" ") ,ylab="Number of Plots", xlab="Standard Deviaiton", cex=0.75)  
 hist(x$NumObs, main=paste("Sensor", x$sensor_ID[1], experiment_id , sep= " "), sub=paste(x$sampling_Date[1] ,sep=" ") ,ylab="Number of Plots", xlab="Number of Observations", cex=0.75)
  hist(x$CV, main=paste("Sensor", x$sensor_ID[1], experiment_id , sep= " "), sub=paste( x$sampling_Date[1] ,sep=" ") ,ylab="Number of Plots", xlab="%CV", cex=0.75)
})
}else{sum_assigned_NDVI[,1:7]}
```
\pagebreak

IRT plot level data:

```{r plot_level_IRT, global.par=FALSE,echo=FALSE,message=FALSE, warning=FALSE,fig.height=8, fig.width=8}
if(nrow(plots)>50){
  par(mfrow=c(2,2))
    d_ply(sum_assigned_IRT, .(), .fun=function(x){
  hist(x$MeanOb, main=paste("Sensor", x$sensor_ID[1], experiment_id , sep= " "), sub=paste(x$sampling_Date[1] ,sep=" ") ,ylab="Number of Plots", xlab="Mean Observation", cex=0.75) 
#  hist(x$Variance, main=paste("Sensor", x$sensor_ID[1], experiment_id, sep=" "),sub=paste(x$sampling_Date[1] ,sep=" ") ,ylab="Number of Plots", xlab="Variance of plosts", cex=0.75)
 hist(x$STDEV, main=paste("Sensor", x$sensor_ID[1], experiment_id , sep= " "), sub=paste( x$sampling_Date[1] ,sep=" ") ,ylab="Number of Plots", xlab="Standard Deviaiton", cex=0.75)  
 hist(x$NumObs, main=paste("Sensor", x$sensor_ID[1], experiment_id , sep= " "), sub=paste(x$sampling_Date[1] ,sep=" ") ,ylab="Number of Plots", xlab="Number of Observations", cex=0.75)
  hist(x$CV, main=paste("Sensor", x$sensor_ID[1], experiment_id , sep= " "), sub=paste( x$sampling_Date[1] ,sep=" ") ,ylab="Number of Plots", xlab="%CV", cex=0.75)
})
}else{sum_assigned_IRT[,1:7]}
```
